PANCHANGE_data_preprocessing

### 2020-08-07 PANCHANGE_data_preprocessing2020-07-15.Rmd
corrected the coping and the ocir file path

# Create vector with items that are included in sum score
ocir.items_prepan = c(
  "ocir.i_repeatedly_check_doors_windows_drawers_etc_prepan",
  "ocir.arranged_things_change_upset_prepan",
  "ocir.repeat_feel_numbers_prepan",
  "ocir.clean_simply_wash_feel_prepan",
  "ocir.mind_upset_unpleasant_thoughts_prepan",
  "ocir.afraid_avoid_throwing_things_prepan",
  "ocir.light_switches_water_taps_prepan",
  "ocir.arranged_things_prepan",
  "ocir.good_feel_bad_numbers_prepan",
  "ocir.hands_longer_wash_prepan",
  "ocir.saved_things_prepan",
  "ocir.frequently_difficulty_rid_nasty_prepan",
  "ocir.i_check_things_more_often_than_necessary_prepan",
  "ocir.arranged_properly_objects_upset_prepan",
  "ocir.feel_compelled_count_things_prepan",
  "ocir.strangers_touch_touched_difficult_prepan",
  "ocir.control_difficult_find_thoughts_prepan",
  "ocir.i_collect_things_i_dont_need_prepan"
  )

>>>>

# Create vector with items that are included in sum score
ocir.items_prepan = c(
  "ocir.i_repeatedly_check_doors_windows_drawers_etc_prepan_numeric",
  "ocir.arranged_things_change_upset_prepan_numeric",
  "ocir.repeat_feel_numbers_prepan_numeric",
  "ocir.clean_simply_wash_feel_prepan_numeric",
  "ocir.mind_upset_unpleasant_thoughts_prepan_numeric",
  "ocir.afraid_avoid_throwing_things_prepan_numeric",
  "ocir.light_switches_water_taps_prepan_numeric",
  "ocir.arranged_things_prepan_numeric",
  "ocir.good_feel_bad_numbers_prepan_numeric",
  "ocir.hands_longer_wash_prepan_numeric",
  "ocir.saved_things_prepan_numeric",
  "ocir.frequently_difficulty_rid_nasty_prepan_numeric",
  "ocir.i_check_things_more_often_than_necessary_prepan_numeric",
  "ocir.arranged_properly_objects_upset_prepan_numeric",
  "ocir.feel_compelled_count_things_prepan_numeric",
  "ocir.strangers_touch_touched_difficult_prepan_numeric",
  "ocir.control_difficult_find_thoughts_prepan_numeric",
  "ocir.i_collect_things_i_dont_need_prepan_numeric"
  )
